04_DESeq_sexes

### 2019-12-23 analysis/04_LDA.Rmd
desc

df2 <- LDA.hyp %>% 
  group_by(treatment,predictedstage) %>%
  summarize(n = n()) %>%
  mutate(tissue = "hypothalamus") 
kable(df2)

@@

df4  <- LDA.pit %>% 
  group_by(treatment,predictedstage) %>%
  summarize(n = n()) %>%
  mutate(tissue = "pituitary")
kable(df4)

@@

df6 <- LDA.gon %>% 
  group_by(treatment,predictedstage) %>%
  summarize(n = n()) %>%
  mutate(tissue = "gonads")
kable(df6)
```

>>>>

df2 <- LDA.hyp %>% 
  group_by(treatment,predictedstage) %>%
  summarize(n = n()) %>%
  mutate(tissue = "hypothalamus")  %>%
  arrange(tissue, treatment, desc(n))
kable(df2)

@@

df4  <- LDA.pit %>% 
  group_by(treatment,predictedstage) %>%
  summarize(n = n()) %>%
  mutate(tissue = "pituitary") %>%
  arrange(tissue, treatment, desc(n))
kable(df4)

@@

df6 <- LDA.gon %>% 
  group_by(treatment,predictedstage) %>%
  summarize(n = n()) %>%
  mutate(tissue = "gonads") %>%
  arrange(tissue, treatment, desc(n))
kable(df6)
```
